Introducing an event-based architecture for concurrent and distributed evolutionary algorithms

### 2018-05-29 paper.tex
Shortens long URLs
Preserving capitalization

  % Yes! we got to the chase 
  Besides these implementations using well known cloud services, there are new computation models for evolutionary algorithms
  that are not functionally equivalent to a canonical EA, but have
  proved to work well in these new environments. Pool based EAs,
  \cite{bollini1999distributed}, with a persistent population that can
  be tapped to retrieve single individuals or pools of them and return
  evaluated or evolved sub-populations, have been used for new
  frameworks such as EvoSpace \cite{García-Valdez2015}, and proved to be
  able to accommodate all kinds of ephemeral and heterogeneous
  resources.

@@

  This paper has been supported in part by
projects TIN2014-56494-C4-3-P (Spanish Ministry of Economy and
Competitiveness) and DeepBio (TIN2017-85727-C4-2-P)

>>>>

  % Yes! we got to the chase 
  Besides these implementations using well known cloud services, there are new computation models for evolutionary algorithms
  that are not functionally equivalent to a canonical EA, but have
  proved to work well in these new environments. Pool based EAs,
  \cite{bollini1999distributed}, with a persistent population that can
  be tapped to retrieve single individuals or pools of them and return
  evaluated or evolved sub-populations, have been used for new
  frameworks such as EvoSpace \cite{Garcia-Valdez2015}, and proved to be
  able to accommodate all kinds of ephemeral and heterogeneous
  resources.

@@

 Supported by
projects TIN2014-56494-C4-3-P (Spanish Ministry of Economy and
Competitiveness) and DeepBio (TIN2017-85727-C4-2-P)
